Trifunctional Phosphatidylinositol 3,4,5-*bis*phosphate

### 2025-02-26 Background/DataAnalysisAndStatistics.qmd
Berit made us new structure figures, new text in data background section

#### Gene Ontology CNET maps

>>>>

#### Gene Ontology Concept Network (CNET) Plots

* Visualizes the relationships between genes and biological gene ontology terms as a network. Concepts (cellular compartment, molecular function, biological process) are arranged as hub nodes with all related genes arrayed as connecting nodes. Genes associated with multiple concepts can be connected to several concept nodes, highlighting the intersection of the concepts.

### 2025-02-26 LipidProbe/PhosphatidicAcid.qmd
new links on index.qmd, reduced library redundancy
Berit made us new structure figures, new text in data background section

:::{.border}
![](/LipidProbe/Structures/PhosphatidicAcid_Structure.png)
:::

@@

## intitialize libraries
library(dplyr)
library(tidyr)
library(plotly)
library(ggplot2)
library(grid)
library(readr)
library(rmarkdown)
library(emojifont)
library(gt)
library(crosstalk)
library(DT)
library(here)

>>>>

:::{.border}
![Trifunctional Phosphatidic Acid](/LipidProbe/Structures/TF_PA.png)
:::

@@

## intitialize libraries
library(here)

### 2025-02-26 LipidProbe/PhosphatidylinositolTrisphosphate.qmd
EOD
Spent all day learning how to make my heatmap look less bad
Berit made us new structure figures, new text in data background section

---
title: "Trifunctional Phosphatidylinositol 3,4,5-*bis*phosphate"
subtitle: "PI(3,4,5)P~3~"
---

@@

>>>>

---
title: "Trifunctional Phosphatidylinositol 3,4,5-*bis*phosphate"
subtitle: "PI(3,4,5)P~3~"
prefer-html: true
---

@@

:::{.border}
![Trifunctional Phosphatidylinositol 3,4,5-*bis*phosphate](/LipidProbe/Structures/TF_PI(3,4,5)P3.png)
:::
